A highly-available move operation for replicated trees

### 2019-06-19 paper/move-op.tex
Paper edits from Alastair's feedback

In our opinion, the only reasonable outcomes are those shown in Figure~\ref{fig:move-same-item}c and~\ref{fig:move-same-item}d: the moved subtree appears either in replica 1's destination location or in replica 2's destination location, but not in both.
Which one of these two is picked is arbitrary, due to the symmetry between the two replicas.
For example, the ``winning'' location could be picked based on a timestamp in the operations, similarly to the ``last writer wins'' conflict resolution method of Thomas's write rule~\cite{Johnson:1975we}.
All replicas pick the same operation as winner, and effectively ignore the conflicting operation.

@@

@@

\subsection{Distributed filesystems}

>>>>

In our opinion, the only reasonable outcomes are those shown in Figure~\ref{fig:move-same-item}c and~\ref{fig:move-same-item}d: the moved subtree appears either in replica 1's destination location or in replica 2's destination location, but not in both.
Which one of these two is picked is arbitrary, due to the symmetry between the two replicas.
For example, the ``winning'' location could be picked based on a timestamp in the operations, similarly to the ``last writer wins'' conflict resolution method of Thomas's write rule~\cite{Johnson:1975we}.
All replicas pick the same operation as winner, and effectively ignore the conflicting operation.
(The \emph{timestamp} in this context need not come from a physical clock; it could also be logical, such as a Lamport timestamp~\cite{Lamport:1978jq}.)

@@

\subsubsection{File merging}\label{sec:files}

In a distributed filesystem, replication and conflict resolution is required not only for the directory structure, but also for the contents of individual files.
This can be accomplished by using CRDTs for file contents as well.
For example, we have explored CRDT algorithms for applications using a JSON data model~\cite{Kleppmann:2016ve} and implemented them in a library called Automerge~\cite{Automerge}.
We discuss distributed filesystems further in Section~\ref{sec:filesystems}.

@@

\subsection{Distributed filesystems}\label{sec:filesystems}
